Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.tex
Move figures into paper folder

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, sharp corners, breakable, frame hidden]}{\end{tcolorbox}}\fi

>>>>

\title[]{Bayesian regression facilitates quantitative modelling of cell
metabolism}
\makeatletter
\begin{document}
\maketitle
\begin{abstract}
This paper presents Maud, a command-line application that implements
Bayesian statistical inference for kinetic models of biochemical
metabolic reaction networks. Maud takes into account quantitative
information from omics experiments and background knowledge, as well as
structural information about kinetic mechanisms, regulatory interactions
and enzyme knockouts. Our paper reviews the existing options in this
area, presents a case study illustrating how Maud can be used to analyse
a metabolic network and explains the biological, statistical and
computational design decisions underpinning Maud.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
